\Huge Conferences in an Era of Expensive Carbon

### 2019-06-19 main.tex
Some more work on transitions

ACM can provide tools to measure emissions. As a start, SIGPLAN (the special
interest group on programming languages) recently worked with ACM's SIG
Governing Board to develop an air-travel-focused CO2e calculator for
conferences. Users can upload conference registration data, and the
calculator will estimate the CO2e cost of air travel for those sufficiently
far away. This calculator could be expanded to account for other conference
emissions.

@@

@@

Indeed, a preliminary analysis that we have done with registration data for
recent SIGPLAN conferences raises as many questions as it answers.
\bcp{Talk about our data analysis, and how it could provide help with
  this. We've started, and see that the situation is not very
  clear. Describe some of our data.  Show the two diagrams.  Draw some
  conclusions / discuss why it's hard to draw conclusions.  (This would be a
  good place to refer to~\cite{ClimateCommitteReport}---we can enumerate
  some of the alternatives that one might have hoped the data would help us
  choose between.)}

\bcp{Tricky transition here.  I think the point we want to make is that
  these decisions are genuinely hard and painful, which is exactly what our
  data shows.}

>>>>

@@

ACM can provide tools for gathering and publicizing this data. As a start,
SIGPLAN (the special interest group on programming languages) recently
worked with ACM's SIG Governing Board to develop an air-travel-focused CO2e
calculator for conferences. Users can upload conference registration data,
and the calculator will estimate the CO2e cost of air travel for those
sufficiently far away. This calculator could be expanded to account for
other conference emissions.

@@

\begin{figure}[t]
\centering
\includegraphics[width=6in]{SIGPLAN-confs.png}
\includegraphics[width=6in]{ParticipantsOriginAll.png}
\caption{Top: carbon footprint per participant for travel to recent SIGPLAN
  conferences\iflater\bcp{Get better file from the other paper, or get
    better version of this one from Crista.}\fi.  Bottom: Origin of
  participants for each conference.  \bcp{Explain in more detail, once we
    have Crista's new figures.}} 
\label{fig:confs}
\end{figure}

The registration data we've gathered from SIGPLAN conferences illustrates
some of the difficulties.  
%
\bcp{Explain the two diagrams.  Discuss how they can be used to draw
  contradictory conclusions.  E.g., one of the many footprint-reduction
  measures that have been discussed in SIGPLAN~\cite{ClimateCommitteReport}
  is locating conferences near their historical ``center of mass.''  Looking
  at the top diagram, one might thus be tempted to locate all conferences in
  the northeast US or western Europe.  But the bottom figure shows that much
  of the participation in each instance of a conference is local; always
  holding a conference at its ``center of mass'' will damage local
  communities everywhere else.  (Maybe this would be a good place to refer
  to~\cite{ClimateCommitteReport}---we can enumerate some of the
  alternatives that one might have hoped the data would help us choose
  between.)}  
%
\bcp{Maybe we can replace the bottom part of the figure by some clearer way
  of visualizing the observation that much of the attendance at each
  conference is local?  E.g., what if, instead of color-coding the different
  sections of the bars by continent, we instead color-coded them by distance
  traveled (in buckets of 500 miles, say)?}

\bcp{Summary: The data shows why these decisions are genuinely hard and
  painful.}
